---
title: "week_6"
author: "Karla Garibay Garcia"
date: "11/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

## Part 2: rank-based test (Mann Whitney U)

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 14, replace = TRUE)

```

```{r}
hist(gp_1)
hist(gp_2)
```

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
my_mwu
```
P-value of 0.28 means that if the null hyp is true (these samples were drawn from pops w/same median) there is a prob of 28% that we could've found median values at least this different by chance. Not sufficient evidence to reject the null hyp of equal ranks or medians using a sig level of 0.05. 

## Part 3: simple linear regression

### A. Look at it

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, 
                            y = body_mass_g)) +
  geom_point()
```

Looks like a linear relationship between flipper length and body mass makes sense.

### B. Model it

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

summary(penguin_lm)
```
### C. Access model outputs

- The slope is `r round(penguin_lm$coefficient[2],2)` (g / mm)
- The y-intercept is `r round(penguin_lm$coefficient[1],2)` (g)
- The full equation is mass = `r round(penguin_lm$coefficient[2],2)`*(flipper length) + (`r round(penguin_lm$coefficient[1],2)`)

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int

penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef

penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out
```
Simple linear regression was used to explore the relationship b/w penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found ($\beta$ = `r round(penguin_coef,3)`, F(`r penguin_lm_out$df`, `r penguin_lm_out$df.residual`) = `r round(penguin_lm_out$statistic,1)`, p < 0.001) with an R^2^ of `r round(penguin_lm_out$r.squared,3)`.

### D. Explore model assumptions

```{r}
plot(penguin_lm)
```


### E. Visualize the model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, 
                            y = body_mass_g)) +
  geom_point() + 
  geom_smooth(method = "lm", 
              color = "cyan", 
              size = 0.5, 
              fill = "gray10", 
              alpha = 0.5) +
  theme_classic() +
  ggpubr::stat_regline_equation(label.x = 175, 
                                label.y = 5500)
```


### F. Find Pearson's *r* for correlation: 
```{r}
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)

penguins_cor
```
Here, we see there's a strong correlation b/w penguin flipper length and body mass (*r* = `r round(penguins_cor$estimate,2)`, t(`r penguins_cor$parameter`) = `r round(penguins_cor$statistic,2)`, p < 0.001)















